---
title: "TidyVerse CREATE GRAPHIC EXTENSIONS"
author: "TEST FILE"
date: "10/23/2020"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include=FALSE}
library(ggplot2)
mpg
```

```{r }
ggplot(mpg, aes(x = displ, y = hwy)) +  geom_point() 

```
## Introdction
The following example from Five Thirty Eight https://fivethirtyeight.com/features/how-americans-like-their-steak/

```{r }
ggplot(mpg, aes(displ, cty, colour = class)) +  geom_point() 
```



The core tidyverse package includes "readr" and "dplyr"
"readr" provides a fast and friendly way to read rectangular data
"dplyr" provides a grammar of data manipulation, providing a consistent set of verbs that solve the most common data manipulation

```{r}
ggplot(mpg, aes(displ, hwy)) + geom_point(aes(colour = "blue")) 
ggplot(mpg, aes(displ, hwy)) + geom_point(colour = "blue") 
 
```

#### Importing libraries
```{r warning=FALSE}
if(!require('tidyverse'))install.packages('tidyverse')
library (tidyverse)
library(dplyr, warn.conflicts = FALSE) # for cleaning the data
options(dplyr.summarise.inform = FALSE)
```


```{r warning=FALSE}
urlfile="https://raw.githubusercontent.com/fivethirtyeight/data/master/steak-survey/steak-risk-survey.csv"
steakdata<- readr::read_csv(url(urlfile))
head(steakdata)
```

## Rename columns

```{r }
ggplot(mpg, aes(drv, hwy)) + geom_jitter()
ggplot(mpg, aes(drv, hwy)) + geom_boxplot()
ggplot(mpg, aes(drv, hwy)) + geom_violin() 
```

```{r warning=FALSE}
steakdata1 = dplyr::rename(steakdata, 
"lottery" = "Consider the following hypothetical situations: <br>In Lottery A, you have a 50% chance of success, with a payout of $100. <br>In Lottery B, you have a 90% chance of success, with a payout of $20. <br><br>Assuming you have $10 to bet, would you play Lottery A or Lottery B?", 
"smoke_cigs" = "Do you ever smoke cigarettes?" ,
"drink_alcohol" = "Do you ever drink alcohol?", 
"gamble" = "Do you ever gamble?",
"skydiving" = "Have you ever been skydiving?",
"overspeeding" = "Do you ever drive above the speed limit?",
"cheat_patner" = "Have you ever cheated on your significant other?",
"eat_steak" = "Do you eat steak?",
"steak_prep" = "How do you like your steak prepared?",
"hh_income" = "Household Income",
"location" = "Location (Census Region)")
head(steakdata1)
```

```{r }
ggplot(mpg, aes(displ, hwy)) +
  geom_point() +  
  geom_smooth(method = "lm") 

```


## Remove first row

```{r }
ggplot(mpg, aes(displ, hwy)) +
  geom_point()+ 
  facet_wrap(~class) 
steakdata2 <- steakdata1[-c(1), ]
head(steakdata2)
```

```{r}
ggplot(mpg, aes(drv, hwy)) +
  geom_point() 
```




```{r }
ggplot(mpg, aes(displ, hwy)) +  
  geom_point() +  
  geom_smooth() 

```


## Mutate Char variables to Factor

```{r }
ggplot(mpg, aes(displ, hwy)) +  
  geom_point() +  
  geom_smooth(span = 0.2) 

ggplot(mpg, aes(displ, hwy)) +
  geom_point() +
  geom_smooth(span = 1)
```



```{r warning=FALSE}
steakdata3 <- steakdata2 %>% as_tibble() 
steakdata4 <- steakdata3 %>%
  mutate(lottery = as.factor(lottery)) %>%
  mutate(smoke_cigs = as.factor(smoke_cigs)) %>%
  mutate(drink_alcohol = as.factor(drink_alcohol)) %>%
  mutate(gamble = as.factor(gamble)) %>%
  mutate(skydiving = as.factor(skydiving)) %>%
  mutate(overspeeding = as.factor(overspeeding)) %>%
  mutate(cheat_patner = as.factor(cheat_patner)) %>%
  mutate(eat_steak = as.factor(eat_steak)) %>%
  mutate(steak_prep = as.factor(steak_prep)) %>%
  mutate(Gender = as.factor(Gender)) %>%
  mutate(Age = as.factor(Age)) %>%
  mutate(hh_income = as.factor(hh_income)) %>%
  mutate(Education = as.factor(Education)) %>%
  mutate(location = as.factor(location))
  head(steakdata4)
```

